The Weakly Nonlinear Magnetorotational Instability

### 2016-09-02 paper/widegap_mri_paper.tex
more points on coeff plot

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../figures/widegap_coeffs_satampscaling.png}
\caption{Critical parameters $\reym_c$ and $k_c$, and coefficients of the Ginzburg-Landau equation (Equation \ref{eq:gle}) as a function of $Pm$. Note the very weak dependence of the linear ($b$) and diffusive ($h$) coefficients on $Pm$. The saturation amplitude $\alpha_{sat} = \sqrt{b/c}$ of the standard MRI system has a power law dependence on $Pm$ which we measure to be $\alpha_{sat} \sim Pm^{0.777}$. This scaling is driven by the $Pm$ dependence of the nonlinear coefficient $c$.}\label{fig:coefficients}
\end{figure}

@@

When $\xi$ in Equation \ref{eq:unperturbed_matrix_eqns} is not equal to zero, the helical MRI arises. We examine a single fiducial helical MRI case, for the parameters used by \citei{Hollerbach:2005tr}, listed in Table \ref{table:parameters}. The helical MRI is an overstability, so the ansatz linear eigenvector we consider (Equation \ref{eq:ansatz}) is characterized by a complex temporal eigenvalue $\sigma$. For our fiducial parameters, the marginal mode has a frequency $\omega = 0.153$. This means that the helical MRI modes are traveling waves, drifting in the $z$ direction with a phase velocity $\omega/k_c$.

At the conclusion of the weakly nonlinear analysis, we find that the coefficients of Equation \ref{eq:gle} are $b = $, $d = $, and $c = $, i.e. complex. The marginal helical MRI is thus described by a complex GLE. This difference in character between the amplitude equations that modulate the weakly nonlinear standard and helical MRI is a consequence of the same property that makes the helical MRI an overstability. With the introduction of an azimuthal component, the background magnetic field acquires a handedness that is not present in a purely axial field. The helical MRI eigenvectors are therefore free to be out of phase with one another. In our perturbation series, the helical MRI modes interact within and between orders with modes which carry different phases, leading to complex GLE coefficients.

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../figures/widegap_coeffs_satampscaling_fivepoints.png}
\caption{Critical parameters $\reym_c$ and $k_c$, and coefficients of the Ginzburg-Landau equation (Equation \ref{eq:gle}) as a function of $Pm$. Note the very weak dependence of the linear ($b$) and diffusive ($h$) coefficients on $Pm$. The saturation amplitude $\alpha_{sat} = \sqrt{b/c}$ of the standard MRI system has a power law dependence on $Pm$ which we measure to be $\alpha_{sat} \sim Pm^{0.777}$. This scaling is driven by the $Pm$ dependence of the nonlinear coefficient $c$.}\label{fig:coefficients}
\end{figure}

@@

When $\xi$ in Equation \ref{eq:unperturbed_matrix_eqns} is not equal to zero, the helical MRI arises. We examine a single fiducial helical MRI case, for the parameters used by \citei{Hollerbach:2005tr}, listed in Table \ref{table:parameters}. The helical MRI is an overstability, so the ansatz linear eigenvector we consider (Equation \ref{eq:ansatz}) is characterized by a complex temporal eigenvalue $\sigma$. For our fiducial parameters, the marginal mode has a frequency $\omega = 0.153$. This means that the helical MRI modes are traveling waves, moving in the $z$ direction with a phase velocity $\omega/k_c$ = .

At the conclusion of the weakly nonlinear analysis, we find that the coefficients of Equation \ref{eq:gle} are complex. The marginal helical MRI is thus described by a complex GLE. This difference in character between the amplitude equations that modulate the weakly nonlinear standard and helical MRI is a consequence of the same property that makes the helical MRI an overstability. With the introduction of an azimuthal component, the background magnetic field acquires a handedness that is not present in a purely axial field. The helical MRI eigenvectors are therefore free to be out of phase with one another. In our perturbation series, the helical MRI modes interact within and between orders with modes which carry different phases, leading to complex GLE coefficients.
